A Natural Language Processing Approach for the Digitalization of Roaming Agreement

### 2021-09-02 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/DesignedMethodology.tex
01.08.21.4

The starting point of the methodology is the decompression and content extraction of PDF files (each PDF file contains a RA). The file name is used as one of the identifiers of the output file. The next step is to find similarities in document texts so that headers and footers are detected to avoid undesired characters. For that purpose, the mechanism used is the detection of different font sizes and weights. Once the PDF format has been converted to text, headers, and footers as well as undesired characters are removed. It is now possible to perform both \textit{detection} and \textit{comparison}.

The \textit{detection} phase includes a requirement associated with the Amazon Comprehend tool regarding the number of symbols to be sent via REST API. For this reason, the text is segmented into pieces of 100 symbols. For each symbol chunk the API outputs entities, key phrases and sentiment in JavaScript Object Notation (JSON) format \cite{AWS2021}, which must be grouped and further processed. The designed logic collects the most important fields such as: 'BeginOffset', 'EndOffset', 'Score', 'Text', 'Type', 'PartOfSpeech', and 'Tag'. In turn, it adds to these the 'Frequency' field that stores the number of repetitions of the entity stored in the 'Text' field. Once this filtering has been done, entities are sorted according to a logic that defines their relevance degree. The designed logic is particularized according to the type of \textit{variable} to be detected. For instance, for the name of the MNO, the 'Score', 'Frequency', and 'BeginOffset' are prioritized, in addition to verifying the number of occurrences within the key phrases. The detected \textit{variables} are stored to be used later to determine which ones are part of the \textit{variations} or \textit{customized texts}.

>>>>

The starting point of the methodology is the decompression and content extraction of PDF files (each PDF file contains a RA). The file name is used as one of the identifiers of the output file. The next step is to find similarities in document texts so that headers and footers are detected to avoid undesired characters. For that purpose, the mechanism used is the detection of different font sizes and weights. Once the PDF format has been converted to text is removed headers, and footers, as well as undesired characters (e.g., spaces, end-lines), in what is a parsing step. It is now possible to perform both \textit{detection} and \textit{comparison}.

The \textit{detection} phase includes a requirement associated with the Amazon Comprehend tool regarding the number of symbols to be sent via REST API. For this reason, the text is segmented into pieces of 100 symbols. For each symbol chunk the API outputs entities, key phrases and sentiment in JavaScript Object Notation (JSON) format \cite{AWS2021}, which must be grouped and further processed. The designed logic collects the most important fields such as: 'BeginOffset', 'EndOffset', 'Score', 'Text', 'Type', 'PartOfSpeech', and 'Tag'. In turn, it adds to these the 'Frequency' field that indicates the number of repetitions of entities with same the same name, i.e., the same 'Text' field. Once this filtering has been done, entities are sorted according to a logic that defines their relevance degree. The designed logic is particularized according to the type of \textit{variable} to be detected. For instance, for the name of the MNO, the 'Score', 'Frequency', and 'BeginOffset' are prioritized, in addition to verifying the number of occurrences within the key phrases. The detected \textit{variables} are stored to be used later to determine which ones are part of the \textit{variations} or \textit{customized texts}.

### 2021-09-02 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/Introduction.tex
01.08.21.4

\section{Introduction}\label{intro}
The roaming service maintains the persistent connectivity of subscribers in different networks and locations. Roaming describes the capability of a subscriber to access mobile services offered by the visited public mobile network (VPMN) through the home public mobile network (HPMN) when roaming outside the coverage range of the HPMN \cite{Tanaka2013}. However, before ensuring persistent connectivity in VPMN the Mobile Network Operators (MNOs) must reach an agreement regarding the technical, commercial and legal relationships known as the Roaming Agreement (RA). In this regard, it is possible to establish three stages within the RA: \textit{drafting}, \textit{testing} and \textit{implementation}. On the one hand, the testing and implementation phases are straightforward as they are focused on implementing what is agreed on the \textit{drafting} phase. On the other hand, the \textit{drafting} phase is ambiguous and involves multiple iterations of the exchange of draft text and proposed articles between both parties, i.e. the MNOs.

>>>>

\section{Introduction}\label{intro}
The roaming service maintains the persistent connectivity of subscribers in different networks and locations. Roaming describes the capability of a subscriber to access mobile services offered by the visited public mobile network (VPMN) through the home public mobile network (HPMN) when roaming outside the coverage range of the HPMN \cite{Tanaka2013}. However, before ensuring persistent connectivity in VPMN the Mobile Network Operators (MNOs) must reach an agreement regarding the technical, commercial and legal relationships known as the Roaming Agreement (RA). In this regard, it is possible to establish three stages within the RA: \textit{drafting}, \textit{testing} and \textit{implementation}. On the one hand, the \textit{testing} and \textit{implementation} phases are straightforward as they are focused on implementing what is agreed on the \textit{drafting} phase. On the other hand, the \textit{drafting} phase is ambiguous and involves multiple iterations of the exchange of draft text and proposed articles between both parties, i.e. the MNOs.

### 2021-09-02 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/RelatedWork.tex
01.08.21.4

Additionally, the scientific literature addresses text processing systems based on NLP techniques in domains such as the judiciary. Thus, the approach introduced in~\cite{8487847} addresses the process of digitalization in the judicial sectors from archives of judicial records for which the authors have designed a text analysis tool that includes grammatical analysis of documents in English based on NLP techniques. The proposed article also constitutes an important contribution in terms of the design of the linguistic analysis based on NLP techniques. However, it lacks formal evaluation in terms of accuracy of NLP implementation. In addition, the work reported in~\cite{9138070} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information. NLP techniques such as sentence tokenization, word tokenization, removing stopwords and lemmatization are part of the parsing stage of the work. The work constitutes a valuable contribution in terms of design and implementation of the tool, however, it lacks demonstration of the feasibility of use, as well as determination of the accuracy of the NLP techniques applied. Finally, authors of~\cite{9104105} propose a model for implementing sentimental analysis using Amazon Comprehend. This system performs an audio-to-text transcription and then performs the processing of the obtained text. Although the value of the contribution lies in the use of NLP techniques from the Amazon Comprehend tool, the paper lacks a formal results section, therefore it is difficult to determine the accuracy of the proposed tool.

Although these studies constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecommunication field and even less in the context of a transparent digitalization of the RA. Therefore, and to the best of our knowledge, we can affirm that our work introduces a topic with a high degree of novelty.

>>>>

Additionally, the scientific literature addresses text processing systems based on NLP techniques in domains such as the judiciary. Thus, the approach introduced in~\cite{8487847} addresses the process of digitalization in the judicial sectors from archives of judicial records for which the authors have designed a text analysis tool that includes grammatical analysis of documents in English based on NLP techniques. The proposed article also constitutes an important contribution in terms of the design of the linguistic analysis based on NLP techniques. However, it lacks formal evaluation in terms of accuracy of NLP implementation. In addition, the work reported in~\cite{9138070} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information. NLP techniques such as sentence tokenization, word tokenization, removing stopwords and lemmatization are part of the parsing stage of the work. The work constitutes a valuable contribution in terms of design and implementation of the tool, however, it lacks demonstration of the feasibility of use, as well as determination of the accuracy of the NLP techniques applied. Finally, authors of~\cite{9104105} propose a methodology for implementing sentimental analysis using Amazon Comprehend. This system performs an audio-to-text transcription and then performs the processing of the obtained text. Although the value of the contribution lies in the use of NLP techniques from the Amazon Comprehend tool, the paper lacks a formal results section, therefore it is difficult to determine the accuracy of the proposed tool.

Although these studies constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecommunications field and even less in the context of a transparent digitalization of the RA. Therefore, and to the best of our knowledge, we can affirm that our work introduces a topic with a high degree of novelty.

### 2021-09-02 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/Results.tex
01.08.21.4

\section{Discussion of Results}\label{results}
Our NLP Engine architecture receives PDF files as inputs, and PDF files normally consist of unstructured text. Because of this, undesired characters may remain despite text parsing. Therefore, it is mandatory to determine the \textit{accuracy} of the results obtained once the output JSON file has been populated. For this purpose, two types of experiments have been conducted to determine the \textit{accuracy} of the results. On the one hand, a simple inspection at the sub-article level and on the other hand, a verification based on symbol comparison. The tests were performed on two RA samples of the MNOs Proximus and Orange \cite{proximus}. Each experiment is described below and the results obtained are discussed in the same section.

\subsection{Accuracy determination based on a simple inspection at sub-article level}
The first accuracy analysis consists of visually determining, i.e., human-eye inspection, whether each sub-article of the RA constitutes a \textit{variation}, a \textit{standard clause} or a \textit{customized text} concerning the GSMA standard template. The results obtained are then compared with the values populated in the NLP Engine output file, for the same sub-article. Considering that the results obtained from the simple inspection constitute the observations and the values collected from the sub-articles classification file constitute the predicted values, the following confusion matrices allow us to analyze the results for each sample RA. In this regard, the confusion matrix in Table~\ref{table1} indicates that the \textit{accuracy} at which the 72 sub-articles analyzed are satisfactorily classified by the NLP Engine as \textit{standard clauses}, \textit{variations} or \textit{customized texts} is acceptable. Proof of this is the fact that the main diagonal of the matrix contains the highest number of True Positives. Table~\ref{table3} summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.

@@

Table ~\ref{table2} shows satisfactory results for the NLP Engine's predictive capability, i.e., regarding the \textit{accuracy} at which the NLP Engine correctly classifies the sub-articles as \textit{standard clauses}, \textit{variations}, or \textit{customized texts} for the Orange sample RA. Using the same evaluation criteria, it is observed how the main diagonal of the confusion matrix in Table~\ref{table2} has the highest number of True Positive. Table~\ref{table3} also summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.

@@

\subsection{Accuracy determination based on symbol comparison}
The second accuracy analysis involves establishing a comparison between the sub-articles populated in the output file concerning the sub-articles existing in the input file containing the RAs. This comparison is performed at the symbol level, considering the order of appearance of each symbol. For that purpose, the text comparison tool Countwordsfree (\cite{countwordsfree}) is used by manually copying sub-article by sub-article. For each sub-article, the following values are determined:

@@

The illustrated radar charts allow us to analyze the results for each RA. The radar chart contains in the inner radius the common percentage of symbols between compared sub-articles and in the outer radius the identifier of the compared sub-article. Fig.~\ref{fig3} shows a comparison in terms of the common percentage of symbols between compared sub-articles for the Proximus sample RA. The conclusion that can be reached by simple inspection is that only 11 of the 72, i.e.,  84.7\% of the analyzed sub-articles are affected, mostly by the introduction of undesired characters when the output file was populated.

Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of symbols between the sub-articles compared for the Orange sample RA. In this case, only 7 of the 86, i.e., 91.9\% of the analyzed sub-articles are affected by the introduction of undesired characters when the output file is populated, thus improving the results obtained for the Proximus sample RA.

>>>>

\section{Discussion of Results}\label{results}
Our NLP Engine architecture receives PDF files as inputs, and PDF files normally consist of unstructured text. Because of this, undesired characters may remain despite text parsing. Therefore, it is mandatory to determine the \textit{accuracy} of the results obtained once the output JSON file has been populated. For this purpose, two types of experiments have been conducted to determine the \textit{accuracy} of the results. On the one hand, a simple inspection at the sub-article level and on the other hand, a verification based on symbol comparison. The tests have been performed on two real RA samples from the mobile operators Proximus and Orange \cite{proximus}. Each experiment is described below and the results obtained are discussed in the same section.

\subsection{Accuracy determination based on a simple inspection at sub-article level}
The first accuracy analysis consists of visually determining, i.e., human-eye inspection, whether each sub-article of the RA constitutes a \textit{variation}, a \textit{standard clause} or a \textit{customized text} concerning the GSMA standard template. The results obtained are then compared with the values populated in the NLP Engine output file, for the same sub-article. Considering that the results obtained from the simple inspection constitute the observations and the values collected from the sub-articles classification file constitute the predicted values, the following confusion matrices allow us to analyze the results for each sample RA. In this regard, the confusion matrix in Table~\ref{table1}  shows satisfactory results for the NLP Engine's predictive capability, i.e., regarding the accuracy at which the NLP Engine correctly classifies 61 of 72 analyzed sub-articles as \textit{standard clauses}, \textit{variations} or \textit{customized texts} for the Proximus sample RA. Proof of this is the fact that the main diagonal of the matrix contains the highest number of True Positives. Table~\ref{table3} summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.

@@

Table~\ref{table2} shows satisfactory results for the NLP Engine's predictive capability, i.e., regarding the \textit{accuracy} at which the NLP Engine correctly classifies 79 of the 86 sub-articles as \textit{standard clauses}, \textit{variations}, or \textit{customized texts} for the Orange sample RA. Using the same evaluation criteria, it is observed how the main diagonal of the confusion matrix in Table~\ref{table2} has the highest number of True Positive. Table~\ref{table3} also summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.

@@

\subsection{Accuracy determination based on symbol comparison}
The second accuracy analysis involves establishing a comparison between the sub-articles populated in the output file concerning the sub-articles existing in the input file containing the real RAs. This comparison is performed at the symbol level, considering the order of appearance of each symbol. For that purpose, the text comparison tool Countwordsfree (\cite{countwordsfree}) is used by manually copying sub-article by sub-article. For each sub-article, the following values are determined:

@@

The illustrated radar charts allow us to analyze the results for each RA. The radar chart contains in the inner radius the common percentage of symbols between compared sub-articles and in the outer radius the identifier of the compared sub-article, i.e., the sub-articles contained in the output file. Fig.~\ref{fig3} shows a comparison in terms of the common percentage of symbols between compared sub-articles for the Proximus sample RA. The conclusion that can be reached by simple inspection is that only 11 of the 72, i.e.,  84.7\% of the analyzed sub-articles are affected, mostly by the introduction of undesired characters when the output file was populated.

Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of symbols between the sub-articles compared for the Orange sample RA. In this case, only 7 of the 86, i.e., 91.9\% of the analyzed sub-articles are affected by the introduction of undesired characters when the output file is populated, thus improving the results obtained regarding the RA Proximus sample.
